---
title: "Hauser_Tests"
author: "Emma Hauser"
params:
  today: !r.Sys.Date
#bibliography: HW2_Refs.bib
output: html_document
---
##Tests for data_import function

```{r Data_Import_sourced, echo=T}
source("Data_Import_Function.R")
```

###Test if data_import makes a data.frame object
```{r DataImport_Test, echo=TRUE}
test <- data_import("NameOfCSV", "PDFData")
if(typeof(test) == data.frame)
{
  print("passed")
}else
{
  print("failed")
}
```

###Test that data_import makes dataframe of correct dimensions

```{r DataImport_Test_2, echo=TRUE}
ExpectRows <- 42
ExpectCols <- 16
test <- data_import("NameOfCSV", "PDFData")
if(ncol(test) == ExpectCols && nrow(test) == ExpectRows)
{
  print("passed")
}else
{
  print("failed")
}
```


##Tests for soil_stats function

###Test that soil_stats makes dataframe of correct dimensions
```{r soil_stats_1, echo=TRUE}
ExpectRowsSoil <- 12
ExpectColsSoil <- 5
testStats <- soil_stats(test)
if(ncol(testStats) == ExpectColsSoil && nrow(testStats) == ExpectRowsSoil)
{
  print("passed")
}else
{
  print("failed")
}
```

###Test that soil_stats calculates means correctly

```{r soil_stats_2, echo=TRUE}
ExpectMean <- 4.713 #this is the first mean, which should be in the first column of response variables, column 3, row 1
testStats2 <- soil_stats(test)
if(testStats2[1,3]==ExpectMean)
{
  print("passed")
}else
{
  print("failed")
}
```

###Test that soil_stats calculates realistic correlation value

```{r soil_stats_3, echo=TRUE}
correlRangeMin <- -1
correlRangeMax <- 1
testStats3 <- soil_stats(test)
if(testStats3[,5] > correlRangeMin && testStats3[,5] < correlRangeMax)
{
  print("passed")
}else
{
  print("failed")
}
```


##Tests for soil_plot function